---
title: "DeltaMS Analysis Settings Overview"
date: "`r format(Sys.time(), '%d %B, %Y')`" 
output: html_document
---
___
<style>
  .col2 {
    columns: 2 100px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 100px; /* chrome, safari */
    -moz-columns: 2 100px;    /* firefox */
  }
</style>


```{r child = "TypeofExp1.Rmd", eval = (isoD@TypeofExp == 1), echo = FALSE}
```  

```{r child = "TypeofExp2.Rmd", eval = (isoD@TypeofExp == 2), echo = FALSE}
```

```{r child = "TypeofExp3.Rmd", eval = (isoD@TypeofExp == 3), echo = FALSE}
```

```{r child = "SelectTwoIsotopes.Rmd", eval = (isoD@iOdm == "Select two isotopes" && isoD@TypeofExp !=3), echo = FALSE}
```

$\Delta$ m = **`r isoD@isotopeMassDiff`**    

```{r child = "deltaMmanual.Rmd", eval = (isoD@iOdm == "Set \u0394 m manually" && isoD@TypeofExp !=3), echo = FALSE}
```


Charge for desired ions was set to **`r isoD@charge`**.

___

### Analyzed files:


```{r echo=FALSE}

if(isoD@TypeofExp==1){
options(knitr.kable.NA = "")
namesFolder<-basename(isoD@WD)
filesInfolders<-list.files(isoD@WD, pattern = isoD@MSfilePattern, ignore.case = TRUE)
df<-data.frame(filesInfolders)
names(df)<-paste0(namesFolder,"*")
knitr::kable(df, format = "markdown", row.names = FALSE,align = "c", caption = NULL)
}

if(isoD@TypeofExp==2){
options(knitr.kable.NA = "")
namesFolder<-c(isoD@unLabeledS,isoD@LabeledS)
folderpaths<-as.list(file.path(isoD@WD, namesFolder))
filesInfolders<-lapply(folderpaths, function(i) {list.files(i, pattern = isoD@MSfilePattern, ignore.case = TRUE)})
names(filesInfolders)<-c("unlabeled Samples", "labeled Samples")
filesInfolders<-lapply(filesInfolders, `length<-`, max(lengths(filesInfolders)))
foldertable<-as.data.frame(filesInfolders, optional = TRUE)
foldertableM<-as.matrix(foldertable)
foldertableM<-rbind(paste0(namesFolder,"*"), foldertableM)
knitr::kable(foldertableM, format = "markdown", row.names = FALSE,align = "c", caption =NULL)
  }

if(isoD@TypeofExp==3){
options(knitr.kable.NA = "")
namesFolder<-c(isoD@uC,isoD@lC,isoD@uT,isoD@lT)
folderpaths<-as.list(file.path(isoD@WD, namesFolder))
filesInfolders<-lapply(folderpaths, function(i) {list.files(i, pattern = isoD@MSfilePattern, ignore.case = TRUE)})
names(filesInfolders)<-c("unlabeled Control", "labeled Control", "unlabeled Treatment", "labeled Treatment")
filesInfolders<-lapply(filesInfolders, `length<-`, max(lengths(filesInfolders)))
foldertable<-as.data.frame(filesInfolders, optional = TRUE)
foldertableM<-as.matrix(foldertable)
foldertableM<-rbind(paste0(namesFolder,"*"), foldertableM)
knitr::kable(foldertableM, format = "markdown", row.names = FALSE,align = "c", caption =NULL)
}
```
*Name of folder with MS-files

___  

### Peakdetection  
```{r child = "matchedFilter.Rmd", eval = (isoD@methodPD == "matchedFilter"), echo = FALSE}
```

```{r child = "centWave.Rmd",eval = (isoD@methodPD == "centWave"), echo = FALSE}
``` 

___  

### Grouping
```{r child = "GroupingPerformed.Rmd", eval = (isoD@NrFi > 1), echo = FALSE}
```

```{r child = "NoGroupingPerformed.Rmd", eval = (isoD@NrFi == 1), echo = FALSE}
```

___  
 

### Retention time correction
```{r child = "NoRTcorrectionPerformed.Rmd", eval = (isoD@NrFi == 1), echo = FALSE}
```

```{r child = "peakgroupsLinear.Rmd", eval = (isoD@retMeth == "peakgroups" && isoD@smooth == "linear" && isoD@NrFi > 1), echo = FALSE}
```

```{r child = "peakgroupsLoess.Rmd", eval = (isoD@retMeth == "peakgroups" && isoD@smooth == "loess" && isoD@NrFi > 1), echo = FALSE}
```

```{r child = "obiwarp.Rmd",eval = (isoD@retMeth == "obiwarp" && isoD@NrFi > 1), echo = FALSE}
```
  
___  

### DeltaMS Settings  

|Parameter          | Value                       | Parameter          | Value                      |
|:----              | :----                       | :----              | :----                      |
|Rtwindow           | `r isoD@Rtwindow`           | ppmw               | `r isoD@ppmw`              |
|noiseCutoff        | `r isoD@noiseCutoff`        | monoTol            | `r isoD@monoTol`           |
|enriTol            | `r isoD@enriTol`            | intChoice          | `r isoD@intChoice`         |
|varEQ              | `r isoD@varEQ`              | alpha              | `r isoD@alpha`             |
|numAtom            | `r isoD@numAtom`            | dpeak              | `r isoD@dpeak`             |
|maxLT              | `r isoD@maxLT`              | compareOnlyDistros | `r isoD@compareOnlyDistros`|
Table: **DeltaMS options**    

